One-dimensional Classical Gas in a Harmonic Trap with Repulsive Interaction

### 2017-01-12 Zhiyu.tex
Jan12 PRE format, tex

>>>>

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=5_energydistribution_pre_rev1.eps} 
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=10_energydistribution_pre_rev1.eps}
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/N=20_energydistribution_pre_rev1.eps}
\caption{test}
\end{figure}
